Hazelnut Live: Type-Theoretic Foundations for Running Incomplete Programs

### 2017-09-21 calculus.tex
todo
moving premises around to match other two ap rules more closely
small changes in working on expandablity with @cyrus-
stubbing in hole for how to expand lambdas that are being checked against hole type
filling in todos for ealamhole rule
adding marks to the holes in dhexps. this is present in the agda, but i cant promise absolute coherence between the two this instant. im sure its close, but there may be a little skew as were still working these out.
fixed definition of substitution type assignment

\begin{figure}[!ht]
  \begin{definition}
    $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff $\domof{\sigma} = \domof{\Delta}$ and for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
  \end{definition}
  \caption{substitution type assignment}
\end{figure}

>>>>

\begin{figure}[!ht]
  \begin{definition}
    $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff $\domof{\sigma} = \domof{\Gamma'}$ and for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
  \end{definition}
  \caption{substitution type assignment}
\end{figure}
